\documentclass[]{article}

\usepackage{fullpage}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}

\title{CS251 Final Assignment}
\author{Arnab Bhattacharya}
\date{10th November, 2013}

\newcommand{\comment}[1]{}

\begin{document}

\maketitle

\section{Introduction}

In this sdocument, I describe how the different phases of the assignment have
been completed such that they together form a nice overall package.  The tools
used along with the phases are listed in a table.  The source of
learning for most of these tools is \cite{cs251}.

\\

\section{Phases}

\subsection{Phase-1: Octave}

The {\bf Octave} script {\tt phase1.m generates the data randomly.

\subsection{Phase-2: Perl}

The {\bf Perl} script {\tt phase2.pl} creates the necessary tables and inserts
the data.

\subsection*{Phase-3: MySQL}

The {\b MySQL} script {\tt phase3.sql} computes the total and grades using
database functions.  The grades are calculated based on the formula given in an
equation for $grade.

\subsection*{Phase-4: Formatting (Perl)}

The {\bf Perl} script {\tt phase3.pl} changes the format of the data so that the
next phase becomes easy.

\subsection*{Phase-5: GnuPlot}

The {\bf GnuPlot} script {\tt phase5.gnu} is rather standard.  It produces the
plot as shown in a figure.

\subsection*{Phase-6: \LaTeX}

The {\tt phase6.tex} is this file only and is, thus, a {\emph self-reference!

\subsection*{Phase-7: Bash}

The knowledge of different {\bf Bash} functions and options has made this script
manageable.

\subsection*{Phase-8: Automation (Bash)}

The master file {\tt phase8.sh} keeps everything thing toegther and runs them in
an orderly manner.

\section{Analysis}

It takes little or no effort to get an "F' grade.

\bibliography{abbrv}
\bibliographydata{phase6}

\end{document}

